Logarithmic Space Verifiers on NP-complete

### 2019-11-14 doc/manuscript.tex
Fixed the content proof

@@

Let $\textit{1TAPE}[T(n)]$ denote the family of languages accepted by deterministic one-way Turing machines with $T(n)$ work tape \cite{HM81}. A monotonically increasing function $f$ is not a constant and for every two values $x < y$ in the domain of $f$, then we obtain that $f(x) \leq f(y)$.

\begin{theorem}
\label{closed}
If $T(n)$ is a monotonically increasing function such that
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
\end{theorem}

\begin{proof}
Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some monotonically increasing function $T'(n)$ when
\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes at most $H(n)$ in the work tapes. Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $G(n) \times n$ symbols for some function $G(n) > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way. The existence of such function $G(n) > 1$ is possible because the family of languages $\textit{1TAPE}[T'(n)]$ is a subset of $P$ and thus $G(n) < 2^{n}$ \cite{Pap03}. This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$. We could complete the end of the instance of size at most $G(n) \times n$ with the symbols that were not read during the deterministic two-way logarithmic space reduction just in the same order that appear in the original instance of size $n$.

However, we know in that instance of size at most $G(n) \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right. Therefore, the instance of size at most $G(n) \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with at most $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.

In this way, we obtain that every language in $\textit{1TAPE}[T'(n)]$ has a mapping to a corresponding language in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$. However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ since $T'(n)$ is a monotonically increasing function and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.

Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$. Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance. Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances. Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a monotonically increasing function.
\end{proof}

\begin{theorem}
\label{partially}
$1L \neq 1NL$ under deterministic two-way logarithmic space reduction.
\end{theorem}

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. We can use this result when $T(n)$ is a monotonically increasing function as well \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}

@@

On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

In this way, if $L = NL$ then $2L = 2NL$. However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ under deterministic two-way logarithmic space reduction according to the Theorem \ref{partially}. Indeed, in case of $2L = 2NL$, then every language in $1NL$ is deterministic two-way logarithmic space reduced to a language in $1L$ and viceversa. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

@@

The economy would become vastly more efficient. There would be disruption, including maybe displacing programmers \cite{IMP95}. The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}. Google would have the resources to excel in such a world \cite{IMP95}.

>>>>

\begin{definition}
The class $1LNL$ contains those languages that are decided by a nondeterministic one-way logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves deterministically on $y$ and nondeterministically on $z$.
\end{definition}

\begin{theorem}
\label{partially}
$|1LNL|_{c} > |1L|_{c}$ where $|\ldots|_{c}$ denotes the cardinality. 
\end{theorem}

\begin{proof}
On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1LNL|_{c} > |1L|_{c}$ since $1L \varsubsetneq 1NL$ and $1LNL$ contains $1NL$, because the prefix $y$ of the instance $x = yz$ could be the empty string. On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and another language $L'' \in 1NL$. Hence, we can create the languages $L''' \in 1LNL$ such that
\[L''' =\{yz: y \in L' \textit{ and } z \in L''\}\]
where  $L' \in 1L$ and $L'' \in 1NL$ are the languages that are linked in our bijective relation. In this way, we can create a bijective relation between these languages $L''' \in 1LNL$ and the corresponding language $L' \in 1L$. However, the set $S$ of all these languages $L''' \in 1LNL$ is a proper subset of $1LNL$, because there are languages in $1LNL$ such that they are not in $S$. Nevertheless, we have that $|S|_{c} = |1L|_{c}$ since there is a bijective relation between these two sets, but we know that $S \varsubsetneq 1LNL$ and thus, $|1LNL|_{c} > |1L|_{c}$.
\end{proof}

@@

@@

On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is also simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
\[L' =\{yz: y \in L \textit{ and } z \in NL\}.\]
Therefore, we can deterministic logarithmic space reduce every language $L' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language in $L_{2} \in 1L$ when $L = NL$. In this way, we can make a relation between every language $L_{1} \in 1LNL$ to another language $L_{2} \in 1L$. We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
\[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
and $\sqcup$ is the blank symbol \cite{Pap03}. We can make this because $1LNL$ is enumerable due to $P$ is enumerable and $1LNL \subseteq P$ \cite{Pap03}. However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes. Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation. However, this is not possible according to the Theorem \ref{partially}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

@@
